---
title: "Austen sentiment analysis"
author: "Sofie Thinggaard"
date: 'created on 17 November 2021 and updated `r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

### Installing packages
```{r Installing packages}
#install.packages("tidyverse")
library(tidyverse)
#dir.create("data")
#Austen_MP <- read_csv("data/Austen_MP.csv")
#install.packages("readr")
library(readr)
#install.packages("gutenbergr")
library(gutenbergr)
Austen_gut <- gutenberg_download(141)
library(magrittr)

Austen_gut <- Austen_gut %>% 
  mutate(linenumber= row_number())

write.csv(Austen_gut, "C:/Users/sofie/Desktop/gutenberg_Mansfield.csv")


```

### Defining afinn
```{r Defining afinn}
#install.packages("textdata")
library(tidytext)
#install.packages("tidyr")
library(tidyr)

afinn <- get_sentiments("afinn")

```

### Separating the sentences with women from men
```{r Separating the sentences with women from men}
Austen_women <- Austen_gut %>%
  filter(str_detect(text, "\\bshe\\b") | str_detect(text, "\\bher\\b")) %>%
  filter(!str_detect(text, "\\bhe\\b" ) & !str_detect(text, "\\bhim\\b"))
```

### Women overall afinn sentiment
```{r Women overall afinn sentiment}
Austen_women %>% 
  unnest_tokens(word,text) %>% inner_join(afinn) %>% summarise(sentiment=sum(value))
```

### Median and mean women afinn
```{r Median and mean women afinn}
women_summary_afinn <- Austen_women %>% 
  unnest_tokens(word,text) %>% inner_join(afinn) %>%
  summarise(
    mean_score = mean(value),
    median_score = median(value)
  )
```

### Seeing which words afinn scored
```{r Seeing which words afinn scored}
Austen_sentiment <- Austen_women %>% 
  unnest_tokens(word,text) %>% inner_join(afinn, by = "word")
```

### Which words does afinn not score: finding the words that are in Austen_women but not austen_sentiment
```{r Which words does afinn not score: finding the words that are in Austen_women but not austen_sentiment}
Austen_words <- Austen_women %>% 
  unnest_tokens(word,text) %>% 
  select(word) %>% 
  setdiff(Austen_sentiment %>% select(word))
```

### Removing stop words and finding adjectives
```{r Removing stop words and finding adjectives}
Austen_adjectives <- Austen_words %>% 
  anti_join(stop_words) %>% 
  left_join(parts_of_speech) %>% 
  filter(pos == "Adjective")

write.csv(Austen_adjectives, "C:/Users/sofie/Desktop/Austen.csv")

```

### Doing the same for the men: seperating men from women
```{r Doing the same for the men: seperating men from women}
Austen_men <- Austen_gut %>%
  filter(str_detect(text, "\\bhe\\b") | str_detect(text, "\\bhim\\b")) %>%
  filter(!str_detect(text, "\\bshe\\b") & !str_detect(text, "\\bher\\b"))
```

### Men overall afinn sentiment
```{r Men overall afinn sentiment}
Austen_men %>% 
  unnest_tokens(word,text) %>% inner_join(afinn) %>% summarise(sentiment=sum(value))

```

### Seeing which words afinn scored for men
```{r Seeing which words afinn scored for men}
Austen_sentiment_men <- Austen_men %>% 
  unnest_tokens(word,text) %>% inner_join(afinn)
```

### Median and mean men afinn
```{r Median and mean men afinn}
men_summary_afinn <- Austen_men %>% 
  unnest_tokens(word,text) %>% inner_join(afinn) %>%
  summarise(
    mean_score = mean(value),
    median_score = median(value)
  )
```

### Plot progession graph with afinn: women
```{r Plot progession graph with afinn: women}
chapter_graph <- Austen_sentiment %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "afinn")

chapter_graph %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```

### Plot progession graph with afinn: men
```{r Plot progession graph with afinn: men}
chapter_graph_men <- Austen_sentiment_men %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "afinn")

chapter_graph_men %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")

```

### Sentiments with bing both women and men
```{r Sentiments with bing both women and men}
bing <- get_sentiments("bing")

women_sentiment_bing <- Austen_women %>% 
  unnest_tokens(word,text) %>% inner_join(bing)

men_sentiment_bing <- Austen_men %>% 
  unnest_tokens(word,text) %>% inner_join(bing)

```

### Wordcloud using bing sentiments: women
```{r Wordcloud using bing sentiments: women}
#install.packages("reshape2")
#install.packages("wordcloud")
library(wordcloud)

library(reshape2)

wordcloud_women <- women_sentiment_bing %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray80", "pink"),
                   max.words = 100)

```

### Wordcloud using bing sentiments: men
```{r Wordcloud using bing sentiments: men}
wordcloud_men <- men_sentiment_bing %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray80", "blue"),
                   max.words = 100)

```

### GGplots using bing sentiments: women
```{r GGplots using bing sentiments: women}
women_sentiment_bing %>% 
   count(word, sentiment, sort = TRUE) %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "frequency",
       y = "word")
#add mutate to get in order of highest frequency to lowest instead of random order

```

### GGplots using bing sentiments: men
```{r GGplots using bing sentiments: men}
men_sentiment_bing %>% 
   count(word, sentiment, sort = TRUE) %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "frequency",
       y = "word")
```

### Men overall bing sentiment
```{r Men overall bing sentiment}
men_sentiment_bing %>% 
count(sentiment)
```

### Women overall bing sentiment
```{r Women overall bing sentiment}
women_sentiment_bing %>% 
count(sentiment)
```

